Combined effects of protein expression variance and correlation on multicomponent systems

### 2020-03-05 Manuscript/Manuscript.Rmd
updated

mypal = rev(colorRampPalette(brewer.pal(11, 'RdBu'))(201))

p6 <- as.ggplot(
  Heatmap(cor, 
        col = mypal,
        heatmap_legend_param = list(title = "R"),
        show_column_dend = FALSE,
        show_row_dend = FALSE,
        show_column_names = FALSE,
        show_row_names = FALSE,
        use_raster = TRUE,
        raster_quality = 1)
  )

@@

(p1 / (p3 + p4)) / (p5 + p6) + 
  plot_annotation(tag_levels = "A")

>>>>

p6 <- tibble(R = as_vector(cor[lower.tri(cor)])) %>%
  ggplot(., aes(x = R)) + geom_histogram(bins = 1000) + xlim(-1,1) +
  theme_minimal()

p7 <- as.ggplot(
  Heatmap(cor, 
        col = rev(colorRampPalette(brewer.pal(11, 'RdBu'))(201)),
        heatmap_legend_param = list(title = "R"),
        show_column_dend = FALSE,
        show_row_dend = FALSE,
        show_column_names = FALSE,
        show_row_names = FALSE,
        use_raster = TRUE,
        raster_quality = 1)
  )

@@

(p1 / (p3 + p4)) / (p5 + p6 | p7) + 
  plot_annotation(tag_levels = "A")
